TODO: A Survey of StarCraft AI Techniques

### 2013-02-15 survey.tex
Minor mod about reactive control (in II.B.5 and AIUR's description).

\subsubsection{Task Decomposition}
Playing a  RTS game like Starcraft  can be decomposed  into three main
tasks: 
\begin{itemize}
\item Strategy:  corresponds to the  decision making process.  This is
  the  highest level of  abstraction for  the game  comprehension. RTS
  games   are   all   about   finding   an   efficient   strategy   or
  counter-strategy  against a  given opponent.  It concerns  the whole
  set of  units and buildings  one owns. If  we may allow  ourselves a
  military analogy, strategy is orders given by generals at the HQ. 
\item  Tactics: are  the implementation  of the  current  strategy. It
  implies  army and  building positioning,  movements, timing,  and so
  on.  Tactics concerns a  group of  units. They  are orders  given by
  officers on the battlefield.
\item  Reactive  control:  is  the  implementation  of  tactics.  This
  consists in   moving,    targeting,   firing,    fleeing   during
  battle. Reactive control focuses on  a specific unit. It is soldiers
  applying officers' orders.
\end{itemize}

@@

\begin{itemize}
\item
  BroodwarBotQ\footnote{\url{http://github.com/SnippyHolloW/BroodwarBotQ}}:
  uses  abstraction for  micro-management, and  divide-and-conquer for
  macro-management  and  intelligence  gathering. To  avoid  conflicts
  between modules (since  the individual tasks of each  of the modules
  are not completely independent), BBQ uses an arbitrator.
\item  Nova\footnote{\url{http://nova.wolfwork.com/}}:  is similar  in
  design as  BroodwarBotQ, and uses  abstraction for micro-management,
  and  divide-and-conquer for  macro-management.  The differences  are
  that Nova does not have  an arbitrator to resolve conflicts, but has
  a  higher-level   module  ({\em  strategy   manager}),  which  posts
  information to the blackboard that the rest of modules follow (thus,
  making use of abstraction).
\item
  UAlbertaBot\footnote{\url{http://code.google.com/p/ualbertabot/}}:
  also  uses abstraction  in  micro-management like  the previous  two
  bots. But it  also uses it in macro-management: as  can be seen, the
  production manager sends commands to the building manager, who is in
  charge   of   producing   the   buildings.  This   bot   also   uses
  divide-and-conquer, and  tasks like scouting  and resource gathering
  are managed by separate, independent modules.
\item       Skynet\footnote{\url{http://code.google.com/p/skynetbot/}}:
  makes     extensive     use      of     both     abstraction     and
  divide-and-conquer.  Considering the  decision  making component  of
  Skynet, we  can see a  high level module  that issues commands  to a
  series of  tactics modules. The  collection of tactic  modules queue
  {\em  tasks} (that  are analogous  to the  abstract actions  used in
  SPAR).  Each different  task has  a specific  low level  module that
  knows how to  execute it. Thus, Skynet uses  a 3 layered abstraction
  hierarchy,  and uses  divide-and-conquer  in all  levels except  the
  highest.
\item
  SPAR\footnote{\url{http://www.planiart.usherbrooke.ca/projects/spar/}}:
  only uses abstraction. Its high-level module determines the strategy
  to  use,  and  the  tactical  decision  module  divides  it  into  a
  collection  of {\em  abstract  actions}, that  are  executed by  the
  lower-level modules.
\item  AIUR\footnote{\url{http://code.google.com/p/aiurproject/}}:  is
  mainly divide-and-conquer oriented, for  macro as well as for micro,
  with a  slight abstraction on  macro due to a  SpendManager deciding
  how  to  spend  and  share  resources  among  Base,  Production  and
  Construction Managers.  At the beginning of a  game, the MoodManager
  initializes  a  ``mood''  which  will  influence  both  tactics  and
  strategy. Tactics  are divided into three  independent managers: the
  {\em  Defense Manager},  controlling  military units  when there  is
  nothing special, the {\em  Under Attack Manager}, activated when the
  opponent is attacking our bases,  and the {\em Army Manager}, taking
  control of units when it is time to attack, following a timing given
  by the current mood.
\item  BTHAI\footnote{\url{http://code.google.com/p/bthai/}}:  uses  a
  two-tier  abstraction hierarchy,  where a  collection  of high-level
  modules command a collection of lower-level agents in charge of each
  of  the units.  At  the high-level,  BTHAI uses  divide-and-conquer,
  having   multiple  high-level  modules   issuing  commands   to  the
  lower-level units.
\end{itemize}

@@

One  interesting aspect  of the  seven bots  described above  is that,
while all of them are  reactive at the lower level (reactive control),
most  if  not all  of  them,  are scripted  at  the  highest level  of
abstraction. BTHAI reads build  and squad formations from a predefined
script,  Nova's {\em  Strategy Manager}  is a  predefined finite-state
machine,  BBQ's construction  manager  reads the  build  order from  a
predefined script, and Skynet's  {\em BuildOrder Manager} is basically
a predefined script. Such scripts  describe the strategy that the bots
will use, however,  such strategy is always fixed.  One could see this
pre-scripting  as  if  each  bot defined  a  ``high-level  programming
language'' to  describe Starcraft strategies, and  the bots themselves
are just interpreters of such strategy. Compared to current approaches
for  Chess or Go,  this scripting  seems a  rigid and  inflexible, but
responds  to the  much higher  complexity  of the  Starcraft game.  An
interesting  exception to  that is  UAlbertaBot, which  uses  a search
algorithm in  the {\em Production Manager} to  find near-optimal build
orders.  Another interesting  case  is  AIUR, that  uses  a {\em  Mood
  Manager}  to   randomly  pick  a  mood  among   six  (cheese,  rush,
aggressive, defensive,  macro, fast expand), which  will influence the
build order,  strategy and tactics. All  of them scripted  so far, but
build  orders  can been  modified  but  the  Spend Manager,  following
available resources.  This mood can change during  the game, regarding
the opponent behavior.

>>>>

\subsubsection{Task Decomposition}
Playing a  RTS game like Starcraft  can be decomposed  into three main
tasks: 
\begin{itemize}
\item Strategy:  corresponds to the  decision making process.  This is
  the  highest level of  abstraction for  the game  comprehension. RTS
  games   are   all   about   finding   an   efficient   strategy   or
  counter-strategy  against a  given opponent.  It concerns  the whole
  set of  units and buildings  one owns. If  we may allow  ourselves a
  military analogy, strategy is orders given by generals at the HQ. 
\item  Tactics: are  the implementation  of the  current  strategy. It
  implies  army and  building positioning,  movements, timing,  and so
  on.  Tactics concerns a  group of  units. They  are orders  given by
  officers on the battlefield.
\item  Reactive  control:  is  the  implementation  of  tactics.  This
  consists   in  moving,   targeting,  firing,   fleeing,  hit-and-run
  techniques (aka ``kiting'')  during battle. Reactive control focuses
  on a specific unit. It is soldiers applying officers' orders. 
\end{itemize}

@@

\begin{itemize}
\item
  BroodwarBotQ\footnote{\url{http://github.com/SnippyHolloW/BroodwarBotQ}}:
  uses  abstraction for  micro-management, and  divide-and-conquer for
  macro-management  and  intelligence  gathering. To  avoid  conflicts
  between modules (since  the individual tasks of each  of the modules
  are not completely independent), BBQ uses an arbitrator.
\item  Nova\footnote{\url{http://nova.wolfwork.com/}}:  is similar  in
  design as  BroodwarBotQ, and uses  abstraction for micro-management,
  and  divide-and-conquer for  macro-management.  The differences  are
  that Nova does not have  an arbitrator to resolve conflicts, but has
  a  higher-level   module  ({\em  strategy   manager}),  which  posts
  information to the blackboard that the rest of modules follow (thus,
  making use of abstraction).
\item
  UAlbertaBot\footnote{\url{http://code.google.com/p/ualbertabot/}}:
  also  uses abstraction  in  micro-management like  the previous  two
  bots. But it  also uses it in macro-management: as  can be seen, the
  production manager sends commands to the building manager, who is in
  charge   of   producing   the   buildings.  This   bot   also   uses
  divide-and-conquer, and  tasks like scouting  and resource gathering
  are managed by separate, independent modules.
\item       Skynet\footnote{\url{http://code.google.com/p/skynetbot/}}:
  makes     extensive     use      of     both     abstraction     and
  divide-and-conquer.  Considering the  decision  making component  of
  Skynet, we  can see a  high level module  that issues commands  to a
  series of  tactics modules. The  collection of tactic  modules queue
  {\em  tasks} (that  are analogous  to the  abstract actions  used in
  SPAR).  Each different  task has  a specific  low level  module that
  knows how to  execute it. Thus, Skynet uses  a 3 layered abstraction
  hierarchy,  and uses  divide-and-conquer  in all  levels except  the
  highest.
\item
  SPAR\footnote{\url{http://www.planiart.usherbrooke.ca/projects/spar/}}:
  only uses abstraction. Its high-level module determines the strategy
  to  use,  and  the  tactical  decision  module  divides  it  into  a
  collection  of {\em  abstract  actions}, that  are  executed by  the
  lower-level modules.
\item  AIUR\footnote{\url{http://code.google.com/p/aiurproject/}}:  is
  mainly divide-and-conquer oriented, for  macro as well as for micro,
  with a  slight abstraction on  macro due to a  SpendManager deciding
  how  to  spend  and  share  resources  among  Base,  Production  and
  Construction Managers.  At the beginning of a  game, the MoodManager
  initializes  a  ``mood''  which  will  influence  both  tactics  and
  strategy. Tactics  are divided into three  independent managers: the
  {\em  Defense Manager},  controlling  military units  when there  is
  nothing special, the {\em  Under Attack Manager}, activated when the
  opponent is attacking our bases,  and the {\em Army Manager}, taking
  control of units when it is time to attack, following a timing given
  by the  current mood. This bot  does not manage however  any kind of
  reactive controls so far.
\item  BTHAI\footnote{\url{http://code.google.com/p/bthai/}}:  uses  a
  two-tier  abstraction hierarchy,  where a  collection  of high-level
  modules command a collection of lower-level agents in charge of each
  of  the units.  At  the high-level,  BTHAI uses  divide-and-conquer,
  having   multiple  high-level  modules   issuing  commands   to  the
  lower-level units.
\end{itemize}

@@

One  interesting aspect  of the  seven bots  described above  is that,
while all  of them  - except AIUR  - are  reactive at the  lower level
(reactive  control), most  if not  all of  them, are  scripted  at the
highest level  of abstraction. BTHAI reads build  and squad formations
from  a  predefined  script,   Nova's  {\em  Strategy  Manager}  is  a
predefined finite-state machine,  BBQ's construction manager reads the
build  order from a  predefined script,  and Skynet's  {\em BuildOrder
  Manager} is basically a predefined script. Such scripts describe the
strategy  that the  bots will  use, however,  such strategy  is always
fixed.   One could see  this pre-scripting  as if  each bot  defined a
``high-level programming language''  to describe Starcraft strategies,
and   the   bots   themselves    are   just   interpreters   of   such
strategy.  Compared  to  current  approaches  for Chess  or  Go,  this
scripting  seems a  rigid and  inflexible,  but responds  to the  much
higher complexity of the  Starcraft game.  An interesting exception to
that  is  UAlbertaBot, which  uses  a  search  algorithm in  the  {\em
  Production  Manager}  to find  near-optimal  build orders.   Another
interesting case is  AIUR, that uses a {\em  Mood Manager} to randomly
pick  a mood among  six (cheese,  rush, aggressive,  defensive, macro,
fast  expand), which  will  influence the  build  order, strategy  and
tactics.  All of  them  scripted so  far,  but build  orders can  been
modified but  the Spend Manager, following  available resources.  This
mood can change during the game, regarding the opponent behavior.
